FictionEro2 - Determinants of Reality Beliefs

### 2025-06-17 study2/analysis/2_emotion.qmd
minor

---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: inline
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant"
    ) |> 
    datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor)) |>
  mutate(ConditionBelief = as.factor(ConditionBelief))

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

@@

df$BAIT_Positive <- (df$BAIT_Exciting + df$BAIT_Benefit)/2
```
**Note**: [The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)

@@

To summarise, **women** rate stimuli on average **significantly lower** in arousal, enticiment and valence than **men**.

@@

This model evaluate ths the effects of Gender and Sexual Orientation on Arousal, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**.

There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.

@@

This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**.

There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.

@@

This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants. The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**.

There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.

@@

This model examines the effect of **Gender Sexual Orientation and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).

<!-- The intercept is Male and photograph.  -->
Women rated 'photographs' significantly lower in arousal than men. Men rated 'photographs' significantly higher in arousal than 'AI-generated' images.

The analysis also examined the average marginal effect of the variable "Condition" (comparing AI-Generated to Photograph) separately for males and females. For males, the arousal is on average significantly lower (althoug only slighly) for AI-Generated images compared to Photograph images. For females, the arousal is on average slightly lower for AI-Generated images compared to Photograph images; however, this effect is not significant.

```{r Arousal Model}

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
                                (1| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_arousal)

marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") 
# > results_table()

@@

```{r Arousal Believed}
m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (1|Participant) + (1|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

@@

This model examines how **Gender and Condition influence enticement** ratings, treating participant and items as random intercepts.

@@

Across both conditions, women rated the images as less enticing overall than men.
There was a significant interaction between gender and image condition, whereby men were less enticed by AI-generated images, whereas women showed no significant difference in enticement based on image condition.

We also analyzed the average marginal effect of the variable “Condition” (comparing AI-Generated to Photograph) separately for males and females. For males, enticement ratings are significantly lower on average for AI-Generated images compared to Photograph  images. For females, enticement ratings are slightly lower on average for AI-Generated images compared to Photograph images, although this difference is not statistically significant.

```{r Enticement Model}
m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
                                   (1 | Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender", re.form=NA)
```

@@

```{r Enticement Believed1}
m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

This model examines the effect of **Gender and Condition on Valence** ratings, while accounting for random variability due to participants and items (i.e., random intercepts).

<!-- The intercept is Male and photograph.  -->
Male participants rated images labelled as AI-Generated significantly lower in valence than Real images. For females, there is no significant effect.

```{r Valence Model}
m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / Condition + 
                                (1| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender", re.form=NA)
```

@@

```{r Valence Believed1}
m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (1| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

This model looks at the effect of **Gender and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).

The results show males rate AI-Generated images lower in emotionality compared to photographs.

```{r Emotionality Model}
m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

marginaleffects::avg_slopes(m, variables="Condition", by="Gender", re.form=NA)
```

@@

```{r EMotionality Believed1}
m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

**Gender Differences**

- Main manipulation worked for men only - i.e., reality manipulation on the nature of the stimuli on subjective ratings

- Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement. Females showed no significant difference in ratings between AI-generated and photographic images across all outcomes.

- Women rate stimuli on average lower in arousal, enticement and valence than men, however this difference was not significant.

@@

- For women, **positive attitudes towards AI** moderated arousal and enticement, resulting in **more favorable evaluations of AI-generated images**. Negative attitudes moderated valence ratings, leading to less favorable evaluations.

- **negative attitudes towards AI** moderated valence ratings for both genders

- Reporting having **higher knowledge about AI** moderated valence ratings for men

- **Sexual activity** moderated enticement ratings for females. Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.

- Men’s **perceptions of the attractiveness of AI-generated images** moderated both arousal and valence ratings. More attractive AI images were rated as more arousing and valent.

- Female's feedback that **no images were attractive** moderated arousal ratings.

@@

pred1 <- rbind(
  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  marginaleffects::avg_predictions(m_enticement, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  marginaleffects::avg_predictions(m_valence, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

stars1 <- data.frame(label=c("**", "***", "**"),
                    Gender=fct_relevel(c("Male", "Male", "Male"), "Male"),
                    Outcome=c("Arousal", "Enticement", "Valence"),
                    y=c(0.55, 0.58, 0.62))

p1 <- pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=Outcome, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
            aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(~Gender, switch="y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:",
       tag = "A")

@@

1. 'Other' was removed due to the very small percentage of individuals identifying as such.
2. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
3. Missing final figures and interpretation of belief as influencing emotional ratings of images

>>>>

---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant"
    ) |> 
    datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor)) |>
  mutate(ConditionBelief = as.factor(ConditionBelief)) |>
  mutate(StimuliType = case_when(
    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
    TRUE ~ "Individual")) |>
  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

@@

df$BAIT_Positive <- (df$BAIT_Exciting + df$BAIT_Benefit)/2
```

@@

To summarise, **women** rate stimuli on average **significantly lower** in arousal, enticiment and valence than **men**. There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on subjective ratings.

@@

This model evaluate ths the effects of Gender and Sexual Orientation on Arousal, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**. There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.

@@

This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**. There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on enticement ratings.

@@

This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants. The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**. There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.

@@

This model examines the effect of **Gender Sexual Orientation, stimuli type, and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts) and condition as random slope for participants.

<!-- The intercept is Male, photograph, individuals  -->

Women rate photograph of individuals lower than males. Men show less arousal toward couple images (vs individual ones), regardless of condition. Women show greater arousal toward couple images than individual ones. Men show less arousal for AI-generated individual images compared to photographic individual images.

Looking at average slopes:
1. Males rate AI-generated images ~0.014 lower in arousal (on average) than photos — significant.
2. Females also rate AI images lower, but not significantly.
3. Males rate couple images significantly lower in arousal than individual ones.
4. Females rate couple images significantly higher in arousal than individual ones.

```{r Arousal with Stimuli Type}

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ StimuliType/ Condition + 
                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_arousal)
marginaleffects::avg_slopes(m_arousal, variables=c("Condition", "StimuliType"), by="Gender") |>
  results_table()

@@

```{r Arousal Believed}
m_a_b <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (Condition|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_a_b)
```

@@

This model examines how **Gender, Stimuli Type and Condition influence enticement** ratings, treating participant and items as random intercepts.

@@

Women rated images as less enticing than men overall. They rated couple images as more enticing than individual images. Men, on the other hand, rated couple images as less enticing. Men also rated AI-generated images as significantly less enticing than photographs, both for images of individual and couple stimuli. In contrast, women did not significantly differentiate between AI and photographic images in terms of enticement.

Looking at the average slopes, both genders rate Ai-generated conditions lower in enticement, although this effect is only significant for men. 
```{r Enticement Model}
m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / StimuliType/ Condition + 
                                   (Condition | Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender") |>
  results_table()

@@

<!-- Note. Adding condition as random slope for participant did not converge -->

```{r Enticement Believed1}
m_e_b <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

This model examines the effect of **Gender, Stimuli Type and Condition on Valence** ratings, while accounting for random variability due to participants and items (i.e., random intercepts).

<!-- The intercept is Male and photograph.  -->
Women rated images overall as lower in valence than men did. They rated couple images as higher in valence than individual ones. Additionally, women rated AI-generated couple images as significantly lower in valence than photographic couple images. Men rated images of couples lower in valence and AI-images of individuals lower in valence comapred to real photos of individuals.

Looking at avergae slopes, both genders rate AI-generated images lower in valence, but this effect is only significant for males.

```{r Valence Model}
m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + 
                                (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender") |>
  results_table()

@@

```{r Valence Believed1}
m_v_b <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_v_b)

@@

This model looks at the effect of **Gender, StimuliType and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).

Females, compared to males, report significantly lower emotionality ratings for fotographs. Among males, couple stimuli are rated lower than individual stimuli.Among females, couple stimuli are rated higher than individual stimuli. For males, AI-generated individual stimuli are rated lower than human-generated ones. Females have lower ratings for AI-generated couple stimuli compared to AI-generated stimuli of individuals.

```{r Emotionality Model}
m_em <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_em)

marginaleffects::avg_slopes(m_em, variables="Condition", by="Gender", re.form=NA) |>
  results_table()
```

@@

```{r EMotionality Believed1}
m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

- Gender is a major predictor of arousal, enticement and valence, with females generally reporting lower ratings than males overall.
- Women prefer couple images (i.e.,significantly higher arousal, enticement and valence ratings); men prefer individual images (i.e.,significantly lower arousal, enticement and valence ratings). 
- AI-generation reduces arousal for men, especially for individual images. AI-generation has no significant effect on arousal for women, whether images are of individuals or couples.

@@

- For women, positive attitudes towards AI moderated arousal and enticement, resulting in more favorable evaluations of AI-generated images. Negative attitudes moderated valence ratings, leading to less favorable evaluations.
- Negative attitudes towards AI moderated valence ratings for both genders
- Reporting having higher knowledge about AI moderated valence ratings for men
- Sexual activity moderated enticement ratings for females. Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
- Men’s perceptions of the attractiveness of AI-generated images moderated both arousal and valence ratings. More attractive AI images were rated as more arousing and valent. 
- Female's feedback that no images were attractive moderated arousal ratings.

@@

pred1 <- rbind(
  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  marginaleffects::avg_predictions(m_enticement, by=c("Gender","StimuliType",  "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  marginaleffects::avg_predictions(m_valence, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

stars1a <- data.frame(label=c("**","***", "**", "***", "***"),
                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Female"), "Male"),
                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence"),
                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
                    x=c(1.5, 1.5, 1.5, 1.5, 1.5), 
                    y = c(0.52, 0.40, 0.57, 0.51, 0.6))

stars1b <- data.frame(label=c("*","**", "*","*"),
                    Gender=fct_relevel(c("Male", "Male", "Male","Female"), "Male"),
                    Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
                    x=c(1, 1, 2, 2),
                    y=c(0.58, 0.63, 0.54, 0.6))

p1 <- pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=StimuliType, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2, key_glyph = "path") +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
  geom_text(data=stars1a, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Gender, switch="y", scales ="free") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:")

@@

1. Models for arousal, enticement, and valence had singularity issues when also adding condition as random slope for stimuli
2. 'Other' was removed due to the very small percentage of individuals identifying as such.
3. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
4. Missing final figures and interpretation of belief as influencing emotional ratings of images
5.[The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)

### 2025-06-17 study2/analysis/3_realness.qmd
minor

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_", "BAIT_")), COPS_Frequency, SexualActivity,-Feedback_Text),
    by = "Participant"
    ) |> 
  datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         SexualOrientation = fct_relevel(SexualOrientation,"Heterosexual", "Homosexual", "Bisexual"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"),
         RealnessBelief = ifelse(Realness > 0.5, 1, 0)) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor))

@@

@@

m <- make_model("Realness ~ Gender / Condition + 
                (1|Participant) + (1|Stimulus)",
                family=glmmTMB::ordbeta())

@@

m <- make_model("RealnessBelief ~ Gender / Condition + 
                (1|Participant) + (1|Stimulus)",
                family="binomial")

@@

predbeta |> 
  ggplot(aes(x=Condition, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2)) +
  scale_color_manual(values=c("red", "blue"), guide="none") +
  facet_grid(~Gender)
```

>>>>

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_", "BAIT_")), COPS_Frequency, SexualActivity,-Feedback_Text),
    by = "Participant"
    ) |> 
  datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         SexualOrientation = fct_relevel(SexualOrientation,"Heterosexual", "Homosexual", "Bisexual"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"),
         RealnessBelief = ifelse(Realness > 0.5, 1, 0)) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor)) |>
  mutate(StimuliType = case_when(
    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
    TRUE ~ "Individual")) |>
  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))

@@

**Note**. Adding StimuliType as a predictor did not change the pattern - Condition was still only a significant predictor for men.

@@

m <- make_model("Realness ~ Gender /Condition + 
                (1|Participant) + (1|Stimulus)",
                family=glmmTMB::ordbeta())

@@

m <- make_model("RealnessBelief ~ Gender /Condition + 
                (1|Participant) + (1|Stimulus)",
                family="binomial")

@@

predbeta |> 
  ggplot(aes(x=Condition, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2)) +
  scale_color_manual(values=c("red", "blue"), guide="none") +
  facet_grid(StimuliType~Gender)
```
